A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-14 final project/Manuscript.Rmd
More work on the final project

```{r, echo=FALSE}
# Similar the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121), n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data = prediction_scores, aes(x = score, y = n)) +
  geom_bar(stat = "identity", fill = "#377eb8") +
  xlab("Number of Correct Predictions") +
  ylab(element_blank()) + 
  xlim(37, 240) +
  annotate("text", x = 65, y = 4, label = "Previous Researchers") +
  geom_vline(xintercept = 238, color = "#e41a1c", linetype="dashed") +
  annotate("text", x = 220, y = 4, label = "Maximum") +
  geom_vline(xintercept = final_model$correct, color = "#4daf4a") +
  annotate("text", x = final_model$correct - 20, y = 4, label = "Our Model") +
  ggtitle("Number of Customers Correctly Predicted")
```

The maximum number of potential policy owners that could be found is 238.  Previous researchers identified 95 policy owners on average.  The best preforming model [@Elkan] during the initial challenge identified 121 policy owners.  A meta analysis found that simpler algorithms tended to outpreform more complicated ones [@Putten].

@@

The MOSTYPE variable has 40 customer types.  Not all customer types were statiscally significant predictors.  We identified those with a probability greater than 0.5 to purchase the insurance product as the `LIKELY_CUSTOMER` variable.  Our second model used LIKELY_CUSTOMER and PPERSAUT.

@@

## Correlation Coefficients for Variables of Interest
```{r, echo=FALSE}
vars <- c("CARAVAN", "PPERSAUT", "PBRAND", "APERSAUT", "LIKELY_CUSTOMERS")
temp <- up_train %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)),
         LIKELY_CUSTOMERS = as.numeric(as.character(LIKELY_CUSTOMERS)))
temp <- temp[vars]

pander(cor(temp[vars], temp[vars]))
```

## Data Dictionary

>>>>

The maximum number of potential policy owners that could be found is 238.  Previous researchers identified 95 policy owners on average.  The best preforming model [@Elkan] during the initial challenge identified 121 policy owners.  A meta analysis found that simpler algorithms tended to outpreform more complicated ones [@Putten].  With the benefit of this finding, we set out to create a simple logistic regression model that preforms just as well or better than the original CoIL Challenge cohort.  The model that we found outpreformed the orignal researcher's model in correctly predicting the customers that would purchase the insurance policy.

```{r, echo=FALSE}
# Similar the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121), n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data = prediction_scores, aes(x = score, y = n)) +
  geom_bar(stat = "identity", fill = "#377eb8") +
  xlab("Number of Correct Predictions") +
  ylab(element_blank()) + 
  xlim(37, 250) +
  annotate("text", x = 65, y = 4, label = "Previous Researchers") +
  geom_vline(xintercept = 238, color = "#e41a1c", linetype="dashed") +
  annotate("text", x = 220, y = 4, label = "Maximum") +
  geom_vline(xintercept = final_model$correct, color = "#4daf4a") +
  annotate("text", x = final_model$correct - 20, y = 4, label = "Our Model") +
  ggtitle("Number of Customers Correctly Predicted")
```

@@

The MOSTYPE variable has 40 customer types.  Not all customer types were statiscally significant predictors.  We identified those with a probability greater than 0.5 to purchase the insurance product as the `LIKELY_CUSTOMER` variable.  A figure in the appendix shows all 40 customer types and the probability that they purched the insurance policy.  Our second model only used LIKELY_CUSTOMER and PPERSAUT. Although it only has two variables, the model preformed well.

In evaluating the models we examined we focused on the specificity.  The goal of the CoIL challenge was to accurately predict those would would purchase the insurance policy, so focusing on the model's specificity was the best evaluation metric.

In order to get a better sense of how well the model generalizes, we repeatedly retrained and evaluated the model using diffrent samplings of the dataset.

@@

## Correlation Coefficients for Variables of Interest
```{r, echo=FALSE}
vars <- c("CARAVAN", "MOSTYPE", "PPERSAUT", "PBRAND", "MOSHOOFD", "APERSAUT", "LIKELY_CUSTOMERS")
temp <- up_train %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)),
         LIKELY_CUSTOMERS = as.numeric(as.character(LIKELY_CUSTOMERS)))
temp <- temp[vars]

numeric_vars <- unlist(lapply(temp, is.numeric))

pander(cor(temp[numeric_vars], temp[numeric_vars]))
```

## Data Dictionary for Variables of Interest
